Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-28 wpe.tex
editing

%%FIGURE INTENT
%This figure shows that entropy changs over time with the signal as well as why the regimes for \svd were chosen. 
%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
  \centering

  %\begin{subfigure}{0.3\textwidth}
  %  \includegraphics[width=0.3\textwidth]{figs/svdipcregimescolored.png}
  %  \caption{The instructions per cycle of \svd. Each color corresonds to the different regimes as selected by rapid shifts in WPE, as seen in Figure \ref{fig:svd_wwpe}. From left to right each change in color represents a change in regime for 6 regimes in total. }
 %   \label{fig:svd_ts}
 % \end{subfigure}%
  %\\
 % \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{figs/SVD_wwpe}
    %\caption{The MASE of ARIMA vs weighted permutation entropy. }
  \caption{
[Joshua: I think adding the colored SVD trace to this would be good or putting it above this figure but need to figure how to line them up properly. Also we need to label that the numbers on the bottom of WPE are regimes not instructions...]]The weighted permutation entropy of one run of SVD. The gray bands
    are regions where the window overlaps regimes. The window size used is
    5,000 $\times$ 100,000 instructions and the word length is $4$.[[Joshua:why is $l=4$ and not 5,6 like the rest of the paper?]]For reference the instructions per cycle of \svd are plotted as a ghost behind this plot. Each color on the ghosted time series corresonds to the different regimes as selected by rapid shifts in WPE. From left to right each change in color represents a change in regime for 6 regimes in total.}\label{fig:wwpe}
\end{figure}

>>>>

%%FIGURE INTENT
%This figure shows that entropy changs over time with the signal as well as why the regimes for \svd were chosen. 
%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
  \centering
  %\begin{subfigure}{0.3\textwidth}
  %  \includegraphics[width=0.3\textwidth]{figs/svdipcregimescolored.png}
  %  \caption{The instructions per cycle of \svd. Each color corresonds to the different regimes as selected by rapid shifts in WPE, as seen in Figure \ref{fig:svd_wwpe}. From left to right each change in color represents a change in regime for 6 regimes in total. }
 %   \label{fig:svd_ts}
 % \end{subfigure}%
  %\\
 % \begin{subfigure}{\textwidth}

%Liz commented this image out temporarily so that her mac doesn't hang
%when she scrolls past p12
    \includegraphics[width=\textwidth]{figs/SVD_wwpe}
    %\caption{The MASE of ARIMA vs weighted permutation entropy. }
  \caption{The weighted permutation entropy of one run of
  SVD. The gray bands are regions where the window overlaps
  regimes. The window size used is 5,000 $\times$ 100,000 instructions
  and the word length is $6$. {\color{red} make sure this is actually updated to 6} For reference the instructions per cycle
  of \svd are plotted as a ghost behind this plot. Each color on the
  ghosted time series corresonds to the different regimes as selected
  by rapid shifts in WPE. From left to right each change in color
  represents a change in regime for 6 regimes in
  total.}\label{fig:wwpe}
\end{figure}
